Capstone Movielens Report

### 2025-05-10 reports/capstone-movielens-report.draft4.tex
Draft report updated: describing a function `model.tune.param_range` (in progress)

\begin{noteblock}
The full source code of the functions described below are are available
in the
\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R\#L74}{Model
Tuning} section of the
\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R}{common-helper.functions.R}
script on \emph{GitHub}.

@@

Below is the most significant part of the code of the
\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R\#L116}{tune.model\_param}
function:

@@

@@

\textbf{param\_values:}; \textbf{fn\_tune.test.param\_value:};
\textbf{break.if\_min = TRUE:}; \textbf{steps.beyond\_min = 2:}:.

\begin{itemize}
\tightlist
\item
  \textbf{param\_values:} A list of values to search for the value
  corresponding to the minimum value of the \texttt{RMSE} ;
\item
  \textbf{fn\_tune.test.param\_value:} A function that calculates the
  value of the \texttt{RMSE} for a given parameter value.;
\item
  \textbf{break.if\_min = TRUE:} A Boolean parameter that determines
  whether the function should terminate after completing the number of
  steps specified by the parameter \texttt{steps.beyond\_min}, after the
  minimum value of the \texttt{RMSE} has been found;
\item
  \textbf{steps.beyond\_min = 2:} (takes effect only if
  \texttt{break.if\_min} parameter is \texttt{TRUE}) Specifies the
  number of steps after finding the minimum value of the \texttt{RMSE},
  upon completion of which the function should terminate.
\end{itemize}

@@

The function searches for the parameter value corresponding to the
minimum value of the \texttt{RMSE} from the list of values specified by
the \texttt{param\_values} parameter. During execution, the function
uses a helper function specified by the
\texttt{fn\_tune.test.param\_value} parameter, which calculates the
\texttt{RMSE} value for the given parameter from the list determined by
the \texttt{param\_values} parameter.

\begin{noteblock}
Note that the function assumes that the dependence of the mean square
error on the input parameter is a monotonically decreasing function
until a minimum is reached and monotonically increasing thereafter. That
is, it is assumed to have a unique minimum in the domain of definition.

@@

The function returns a data structure containing the found value of the
input parameter \texttt{param\_values} for which the \texttt{RMSE} value
is minimal, as well as the minimum \texttt{RMSE} value itself, along
with a sequence of all calculated \texttt{RMSE} values.

@@

@@

@@

@@

\subparagraph{`` Function}\label{function-4}

@@

\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-86-1.pdf}

>>>>

\begin{noteblock}
The full source code of the functions described below are available in
the
\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R\#L74}{Model
Tuning} section of the
\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R}{common-helper.functions.R}
script on \emph{GitHub}.

@@

The function searches for the parameter value corresponding to the
minimum value of the \texttt{RMSE} from the list of values specified by
the \texttt{param\_values} parameter.

Sugnature

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{tune.model\_param }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(param\_values, }
\NormalTok{                             fn\_tune.test.param\_value, }
                             \AttributeTok{break.if\_min =} \ConstantTok{TRUE}\NormalTok{,}
                             \AttributeTok{steps.beyond\_min =} \DecValTok{2}\NormalTok{)\{}

\CommentTok{\# ...}
  \FunctionTok{list}\NormalTok{(}\AttributeTok{tuned.result =} \FunctionTok{data.frame}\NormalTok{(}\AttributeTok{RMSE =}\NormalTok{ RMSEs\_tmp,}
                                \AttributeTok{parameter.value =}\NormalTok{ param\_vals\_tmp),}
       \AttributeTok{best\_result =}\NormalTok{ param\_values.best\_result)}
\NormalTok{\}  }
\end{Highlighting}
\end{Shaded}

\hfill\break
- \textbf{param\_values:} A list of values to search for the value
corresponding to the minimum value of the \texttt{RMSE} ; -
\textbf{fn\_tune.test.param\_value:} A helper function that calculates
the value of the \texttt{RMSE} for a given parameter value.; -
\textbf{break.if\_min = TRUE:} A Boolean parameter that determines
whether the function should terminate after completing the number of
steps specified by the parameter \texttt{steps.beyond\_min}, after the
minimum value of the \texttt{RMSE} has been found; -
\textbf{steps.beyond\_min = 2:} (takes effect only if
\texttt{break.if\_min} parameter is \texttt{TRUE}) Specifies the number
of steps after finding the minimum value of the \texttt{RMSE}, upon
completion of which the function should terminate.

\hfill\break
During execution, the function uses a helper function specified by the
\texttt{fn\_tune.test.param\_value} parameter, which calculates the
\texttt{RMSE} value for the given parameter from the list determined by
the \texttt{param\_values} parameter.

\begin{noteblock}
Note that the function assumes that the dependence of the \texttt{RMSE}
on the input parameter is a monotonically decreasing function until a
minimum is reached and monotonically increasing thereafter. That is, it
is assumed to have a single minimum in the domain of definition.

\hfill\break
The function returns a data structure containing the found value of the
input parameter \texttt{param\_values} for which the \texttt{RMSE} value
is minimal, as well as the minimum \texttt{RMSE} value itself, along
with a sequence of all calculated \texttt{RMSE} values.

Source Code

\hfill\break
Below is the most significant part of the code of the
\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R\#L116}{tune.model\_param}
function:

@@

\subparagraph{\texorpdfstring{\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R\#L198}{model.tune.param\_range}
Function}{model.tune.param\_range Function}}\label{model.tune.param_range-function}

The function fine-tunes the model by searching for the best possible
value of the input parameter over a given interval for which the
corresponding \texttt{RMSE} value is minimal.

Sugnature

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{model.tune.param\_range }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(loop\_starter,}
\NormalTok{                             tune\_dir\_path,}
\NormalTok{                             cache\_file\_base\_name,}
\NormalTok{                             fn\_tune.test.param\_value,}
                             \AttributeTok{max.identical.min\_RMSE.count =} \DecValTok{4}\NormalTok{,}
                             \AttributeTok{is.cv =} \ConstantTok{TRUE}\NormalTok{,}
                             \AttributeTok{endpoint.min\_diff =} \DecValTok{0}\NormalTok{, }\CommentTok{\#1e{-}07,}
                             \AttributeTok{break.if\_min =} \ConstantTok{TRUE}\NormalTok{,}
                             \AttributeTok{steps.beyond\_min =} \DecValTok{2}\NormalTok{)\{}
  \CommentTok{\# ...}
  \FunctionTok{list}\NormalTok{(}\AttributeTok{best\_result =}\NormalTok{ param\_values.best\_result,}
       \AttributeTok{param\_values.endpoints =} \FunctionTok{c}\NormalTok{(prm\_val.leftmost, prm\_val.rightmost, seq\_increment),}
       \AttributeTok{tuned.result =} \FunctionTok{data.frame}\NormalTok{(}\AttributeTok{parameter.value =}\NormalTok{ parameter.value,}
                                 \AttributeTok{RMSE =}\NormalTok{ result.RMSE))}
\NormalTok{\}}
\end{Highlighting}
\end{Shaded}

@@

\hfill\break
- \textbf{fn\_tune.test.param\_value:} A helper function that calculates
the value of the \texttt{RMSE} for a given parameter value.; -
\textbf{break.if\_min = TRUE:} A Boolean parameter that determines
whether the function should terminate after completing the number of
steps specified by the parameter \texttt{steps.beyond\_min}, after the
minimum value of the \texttt{RMSE} has been found; -
\textbf{steps.beyond\_min = 2:} (takes effect only if
\texttt{break.if\_min} parameter is \texttt{TRUE}) Specifies the number
of steps after finding the minimum value of the \texttt{RMSE}, upon
completion of which the function should terminate.

@@

\hfill\break
During execution, the function uses a helper function specified by the
\texttt{fn\_tune.test.param\_value} parameter, which calculates the
\texttt{RMSE} value for the given parameter from the list determined by
the inner \texttt{param\_values} sequence.

\begin{noteblock}
Note

@@

Source Code

\hfill\break
Below is the most significant part of the code of the
\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R\#L198}{model.tune.param\_range}
function:

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{model.tune.param\_range }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(loop\_starter,}
\NormalTok{                             tune\_dir\_path,}
\NormalTok{                             cache\_file\_base\_name,}
\NormalTok{                             fn\_tune.test.param\_value,}
                             \AttributeTok{max.identical.min\_RMSE.count =} \DecValTok{4}\NormalTok{,}
                             \AttributeTok{is.cv =} \ConstantTok{TRUE}\NormalTok{,}
                             \AttributeTok{endpoint.min\_diff =} \DecValTok{0}\NormalTok{, }\CommentTok{\#1e{-}07,}
                             \AttributeTok{break.if\_min =} \ConstantTok{TRUE}\NormalTok{,}
                             \AttributeTok{steps.beyond\_min =} \DecValTok{2}\NormalTok{)\{}

\NormalTok{  seq\_start }\OtherTok{\textless{}{-}}\NormalTok{ loop\_starter[}\DecValTok{1}\NormalTok{]}
\NormalTok{  seq\_end }\OtherTok{\textless{}{-}}\NormalTok{ loop\_starter[}\DecValTok{2}\NormalTok{]}
\NormalTok{  range\_divider }\OtherTok{\textless{}{-}}\NormalTok{ loop\_starter[}\DecValTok{3}\NormalTok{]}

  \ControlFlowTok{if}\NormalTok{ (range\_divider }\SpecialCharTok{\textless{}} \DecValTok{4}\NormalTok{) \{}
\NormalTok{    range\_divider }\OtherTok{\textless{}{-}} \DecValTok{4}
\NormalTok{  \}}

\NormalTok{  prm\_val.leftmost }\OtherTok{\textless{}{-}}\NormalTok{ seq\_start}
\NormalTok{  prm\_val.rightmost }\OtherTok{\textless{}{-}}\NormalTok{ seq\_end}

\NormalTok{  RMSE.leftmost }\OtherTok{\textless{}{-}} \ConstantTok{NA}
\NormalTok{  RMSE.rightmost }\OtherTok{\textless{}{-}} \ConstantTok{NA}

\NormalTok{  best\_RMSE }\OtherTok{\textless{}{-}} \ConstantTok{NA}
\NormalTok{  param.best\_value }\OtherTok{\textless{}{-}} \DecValTok{0}

\NormalTok{  param\_values.best\_result }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\AttributeTok{param.best\_value =}\NormalTok{ param.best\_value, }
                                \AttributeTok{best\_RMSE =}\NormalTok{ best\_RMSE)}

  \ControlFlowTok{repeat}\NormalTok{\{}
\NormalTok{    seq\_increment }\OtherTok{\textless{}{-}}\NormalTok{ (seq\_end }\SpecialCharTok{{-}}\NormalTok{ seq\_start)}\SpecialCharTok{/}\NormalTok{range\_divider }

    \ControlFlowTok{if}\NormalTok{ (seq\_increment }\SpecialCharTok{\textless{}} \FloatTok{0.0000000000001}\NormalTok{) \{}
      \FunctionTok{warning}\NormalTok{(}\StringTok{"Function \textasciigrave{}model.tune.param\_range\textasciigrave{}:}
\StringTok{parameter value increment is too small."}\NormalTok{)}

      \FunctionTok{put\_log2}\NormalTok{(}\StringTok{"Function \textasciigrave{}model.tune.param\_range\textasciigrave{}:}
\StringTok{Final best RMSE for \textasciigrave{}parameter value = \%1\textasciigrave{}: \%2"}\NormalTok{,}
\NormalTok{               param\_values.best\_result[}\StringTok{"param.best\_value"}\NormalTok{],}
\NormalTok{               param\_values.best\_result[}\StringTok{"best\_RMSE"}\NormalTok{])}
      \ControlFlowTok{break}
\NormalTok{    \}}

\NormalTok{    test\_param\_vals }\OtherTok{\textless{}{-}} \FunctionTok{seq}\NormalTok{(seq\_start, seq\_end, seq\_increment)}

\NormalTok{    file\_name\_tmp }\OtherTok{\textless{}{-}}\NormalTok{ cache\_file\_base\_name }\SpecialCharTok{|\textgreater{}}
      \FunctionTok{str\_c}\NormalTok{(}\StringTok{"\_"}\NormalTok{) }\SpecialCharTok{|\textgreater{}}
      \FunctionTok{str\_c}\NormalTok{(}\FunctionTok{as.character}\NormalTok{(loop\_starter[}\DecValTok{1}\NormalTok{])) }\SpecialCharTok{|\textgreater{}}
      \FunctionTok{str\_c}\NormalTok{(}\StringTok{"\_"}\NormalTok{) }\SpecialCharTok{|\textgreater{}}
      \FunctionTok{str\_c}\NormalTok{(}\FunctionTok{as.character}\NormalTok{(loop\_starter[}\DecValTok{3}\NormalTok{])) }\SpecialCharTok{|\textgreater{}}
      \FunctionTok{str\_c}\NormalTok{(}\StringTok{"\_"}\NormalTok{) }\SpecialCharTok{|\textgreater{}}
      \FunctionTok{str\_c}\NormalTok{(}\FunctionTok{as.character}\NormalTok{(range\_divider)) }\SpecialCharTok{|\textgreater{}}
      \FunctionTok{str\_c}\NormalTok{(}\StringTok{"."}\NormalTok{) }\SpecialCharTok{|\textgreater{}}
      \FunctionTok{str\_c}\NormalTok{(}\FunctionTok{as.character}\NormalTok{(seq\_start)) }\SpecialCharTok{|\textgreater{}}
      \FunctionTok{str\_c}\NormalTok{(}\StringTok{"{-}"}\NormalTok{) }\SpecialCharTok{|\textgreater{}}
      \FunctionTok{str\_c}\NormalTok{(}\FunctionTok{as.character}\NormalTok{(seq\_end)) }\SpecialCharTok{|\textgreater{}}
      \FunctionTok{str\_c}\NormalTok{(}\StringTok{".RData"}\NormalTok{)}

\NormalTok{    file\_path\_tmp }\OtherTok{\textless{}{-}} \FunctionTok{file.path}\NormalTok{(tune\_dir\_path, file\_name\_tmp)}

    \FunctionTok{put\_log1}\NormalTok{(}\StringTok{"Function \textasciigrave{}model.tune.param\_range\textasciigrave{}:}
\StringTok{File path generated: \%1"}\NormalTok{, file\_path\_tmp)}

    \ControlFlowTok{if}\NormalTok{ (}\FunctionTok{file.exists}\NormalTok{(file\_path\_tmp)) \{}
      \FunctionTok{put\_log1}\NormalTok{(}\StringTok{"Function \textasciigrave{}model.tune.param\_range\textasciigrave{}:}
\StringTok{Loading tuning data from file: \%1..."}\NormalTok{, file\_path\_tmp)}

\NormalTok{      start }\OtherTok{\textless{}{-}} \FunctionTok{put\_start\_date}\NormalTok{()}
      \FunctionTok{load}\NormalTok{(file\_path\_tmp)}
      \FunctionTok{put\_end\_date}\NormalTok{(start)}
      \FunctionTok{put\_log1}\NormalTok{(}\StringTok{"Function \textasciigrave{}model.tune.param\_range\textasciigrave{}:}
\StringTok{Tuning data has been loaded from file: \%1"}\NormalTok{, file\_path\_tmp)}

\NormalTok{      tuned.result }\OtherTok{\textless{}{-}}\NormalTok{ tuned\_result}\SpecialCharTok{$}\NormalTok{tuned.result}

      \ControlFlowTok{if}\NormalTok{(}\FunctionTok{length}\NormalTok{(file\_path\_tmp) }\SpecialCharTok{\textgreater{}} \DecValTok{0}\NormalTok{) \{}
\NormalTok{      \}}
\NormalTok{    \} }\ControlFlowTok{else}\NormalTok{ \{}
\NormalTok{      tuned\_result }\OtherTok{\textless{}{-}} \FunctionTok{tune.model\_param}\NormalTok{(test\_param\_vals, }
\NormalTok{                                        fn\_tune.test.param\_value,}
\NormalTok{                                        break.if\_min,}
\NormalTok{                                        steps.beyond\_min)}

\NormalTok{      tuned.result }\OtherTok{\textless{}{-}}\NormalTok{ tuned\_result}\SpecialCharTok{$}\NormalTok{tuned.result}

      \FunctionTok{save}\NormalTok{(tuned\_result,}
\NormalTok{           param.best\_value,}
\NormalTok{           seq\_increment,}
\NormalTok{           range\_divider,}
           \AttributeTok{file =}\NormalTok{ file\_path\_tmp)}

      \FunctionTok{put\_log1}\NormalTok{(}\StringTok{"Function \textasciigrave{}model.tune.param\_range\textasciigrave{}:}
\StringTok{File saved: \%1"}\NormalTok{, file\_path\_tmp)}
\NormalTok{    \}}

    \FunctionTok{plot}\NormalTok{(tuned.result}\SpecialCharTok{$}\NormalTok{parameter.value, tuned.result}\SpecialCharTok{$}\NormalTok{RMSE)}

\NormalTok{    bound.idx }\OtherTok{\textless{}{-}} \FunctionTok{get\_fine\_tune.param.endpoints.idx}\NormalTok{(tuned.result)}
\NormalTok{    start.idx }\OtherTok{\textless{}{-}}\NormalTok{ bound.idx[}\StringTok{"start"}\NormalTok{]}
\NormalTok{    end.idx }\OtherTok{\textless{}{-}}\NormalTok{ bound.idx[}\StringTok{"end"}\NormalTok{]}
\NormalTok{    best\_RMSE.idx }\OtherTok{\textless{}{-}}\NormalTok{ bound.idx[}\StringTok{"best"}\NormalTok{]}

\NormalTok{    prm\_val.leftmost.tmp }\OtherTok{\textless{}{-}}\NormalTok{ tuned.result}\SpecialCharTok{$}\NormalTok{parameter.value[start.idx]}
\NormalTok{    RMSE.leftmost.tmp }\OtherTok{\textless{}{-}}\NormalTok{ tuned.result}\SpecialCharTok{$}\NormalTok{RMSE[start.idx]}

\NormalTok{    prm\_val.rightmost.tmp }\OtherTok{\textless{}{-}}\NormalTok{ tuned.result}\SpecialCharTok{$}\NormalTok{parameter.value[end.idx]}
\NormalTok{    RMSE.rightmost.tmp }\OtherTok{\textless{}{-}}\NormalTok{ tuned.result}\SpecialCharTok{$}\NormalTok{RMSE[end.idx]}

\NormalTok{    min\_RMSE }\OtherTok{\textless{}{-}}\NormalTok{ tuned.result}\SpecialCharTok{$}\NormalTok{RMSE[best\_RMSE.idx]}
\NormalTok{    min\_RMSE.prm\_val }\OtherTok{\textless{}{-}}\NormalTok{ tuned.result}\SpecialCharTok{$}\NormalTok{parameter.value[best\_RMSE.idx]}

\NormalTok{    seq\_start }\OtherTok{\textless{}{-}}\NormalTok{ prm\_val.leftmost.tmp}
\NormalTok{    seq\_end }\OtherTok{\textless{}{-}}\NormalTok{ prm\_val.rightmost.tmp}

    \ControlFlowTok{if}\NormalTok{ (}\FunctionTok{is.na}\NormalTok{(best\_RMSE)) \{}
\NormalTok{      prm\_val.leftmost }\OtherTok{\textless{}{-}}\NormalTok{ prm\_val.leftmost.tmp}
\NormalTok{      RMSE.leftmost }\OtherTok{\textless{}{-}}\NormalTok{ RMSE.leftmost.tmp}

\NormalTok{      prm\_val.rightmost }\OtherTok{\textless{}{-}}\NormalTok{ prm\_val.rightmost.tmp}
\NormalTok{      RMSE.rightmost }\OtherTok{\textless{}{-}}\NormalTok{ RMSE.rightmost.tmp}

\NormalTok{      param.best\_value }\OtherTok{\textless{}{-}}\NormalTok{ min\_RMSE.prm\_val}
\NormalTok{      best\_RMSE }\OtherTok{\textless{}{-}}\NormalTok{ min\_RMSE}
\NormalTok{    \}}

    \ControlFlowTok{if}\NormalTok{ (RMSE.leftmost.tmp }\SpecialCharTok{{-}}\NormalTok{ min\_RMSE }\SpecialCharTok{\textgreater{}=}\NormalTok{ endpoint.min\_diff) \{}
\NormalTok{      prm\_val.leftmost }\OtherTok{\textless{}{-}}\NormalTok{ prm\_val.leftmost.tmp}
\NormalTok{      RMSE.leftmost }\OtherTok{\textless{}{-}}\NormalTok{ RMSE.leftmost.tmp}
\NormalTok{    \} }

    \ControlFlowTok{if}\NormalTok{ (RMSE.rightmost.tmp }\SpecialCharTok{{-}}\NormalTok{ min\_RMSE }\SpecialCharTok{\textgreater{}=}\NormalTok{ endpoint.min\_diff) \{}
\NormalTok{      prm\_val.rightmost }\OtherTok{\textless{}{-}}\NormalTok{ prm\_val.rightmost.tmp}
\NormalTok{      RMSE.rightmost }\OtherTok{\textless{}{-}}\NormalTok{ RMSE.rightmost.tmp}
\NormalTok{    \} }

    \ControlFlowTok{if}\NormalTok{ (end.idx }\SpecialCharTok{{-}}\NormalTok{ start.idx }\SpecialCharTok{\textless{}=} \DecValTok{0}\NormalTok{) \{}
      \FunctionTok{warning}\NormalTok{(}\StringTok{"\textasciigrave{}tuned.result$parameter.value\textasciigrave{} sequential start index are the same or greater than end one."}\NormalTok{)}
      \ControlFlowTok{break}
\NormalTok{    \}}

    \ControlFlowTok{if}\NormalTok{ (best\_RMSE }\SpecialCharTok{==}\NormalTok{ min\_RMSE) \{}
      \FunctionTok{warning}\NormalTok{(}\StringTok{"Currently computed minimal RMSE equals the previously reached best one: "}\NormalTok{,}
\NormalTok{              best\_RMSE, }\StringTok{"}
\StringTok{Currently computed minial value is: "}\NormalTok{, min\_RMSE)}

      \ControlFlowTok{if}\NormalTok{ (}\FunctionTok{sum}\NormalTok{(tuned.result}\SpecialCharTok{$}\NormalTok{RMSE[tuned.result}\SpecialCharTok{$}\NormalTok{RMSE }\SpecialCharTok{==}\NormalTok{ min\_RMSE]) }\SpecialCharTok{\textgreater{}=}\NormalTok{ max.identical.min\_RMSE.count) \{}
        \FunctionTok{warning}\NormalTok{(}\StringTok{"Minimal \textasciigrave{}RMSE\textasciigrave{}identical values count reached it maximum allowed value: "}\NormalTok{,}
\NormalTok{                max.identical.min\_RMSE.count)}

\NormalTok{        param\_values.best\_result }\OtherTok{\textless{}{-}}
          \FunctionTok{get\_best\_param.result}\NormalTok{(tuned.result}\SpecialCharTok{$}\NormalTok{parameter.value,}
\NormalTok{                                tuned.result}\SpecialCharTok{$}\NormalTok{RMSE)}

        \FunctionTok{put\_log2}\NormalTok{(}\StringTok{"Function \textasciigrave{}model.tune.param\_range\textasciigrave{}:}
\StringTok{      Reached the best RMSE for \textasciigrave{}parameter value = \%1\textasciigrave{}: \%2"}\NormalTok{,}
\NormalTok{                 param\_values.best\_result[}\StringTok{"param.best\_value"}\NormalTok{],}
\NormalTok{                 param\_values.best\_result[}\StringTok{"best\_RMSE"}\NormalTok{])}
        \ControlFlowTok{break}
\NormalTok{      \}}

\NormalTok{    \} }\ControlFlowTok{else} \ControlFlowTok{if}\NormalTok{ (best\_RMSE }\SpecialCharTok{\textless{}}\NormalTok{ min\_RMSE) \{}
      \FunctionTok{stop}\NormalTok{(}\StringTok{"Current minimal RMSE is greater than previously computed best value: "}\NormalTok{,}
\NormalTok{           best\_RMSE, }\StringTok{"}
\StringTok{Currently computed minial value is: "}\NormalTok{, min\_RMSE)}
\NormalTok{    \}}

\NormalTok{    best\_RMSE }\OtherTok{\textless{}{-}}\NormalTok{ min\_RMSE}
\NormalTok{    param.best\_value }\OtherTok{\textless{}{-}}\NormalTok{ min\_RMSE.prm\_val}

\NormalTok{    param\_values.best\_result }\OtherTok{\textless{}{-}} 
      \FunctionTok{get\_best\_param.result}\NormalTok{(tuned.result}\SpecialCharTok{$}\NormalTok{parameter.value, }
\NormalTok{                          tuned.result}\SpecialCharTok{$}\NormalTok{RMSE)}

    \FunctionTok{put\_log2}\NormalTok{(}\StringTok{"Function \textasciigrave{}model.tune.param\_range\textasciigrave{}:}
\StringTok{Currently reached best RMSE for \textasciigrave{}parameter value = \%1\textasciigrave{}: \%2"}\NormalTok{,}
\NormalTok{             param\_values.best\_result[}\StringTok{"param.best\_value"}\NormalTok{],}
\NormalTok{             param\_values.best\_result[}\StringTok{"best\_RMSE"}\NormalTok{])}
\NormalTok{  \}}

\NormalTok{  n }\OtherTok{\textless{}{-}} \FunctionTok{length}\NormalTok{(tuned.result}\SpecialCharTok{$}\NormalTok{parameter.value)}
\NormalTok{  parameter.value }\OtherTok{\textless{}{-}}\NormalTok{ tuned.result}\SpecialCharTok{$}\NormalTok{parameter.value}
\NormalTok{  result.RMSE }\OtherTok{\textless{}{-}}\NormalTok{ tuned.result}\SpecialCharTok{$}\NormalTok{RMSE}

  \ControlFlowTok{if}\NormalTok{ (result.RMSE[}\DecValTok{1}\NormalTok{] }\SpecialCharTok{==}\NormalTok{ best\_RMSE) \{}
\NormalTok{    parameter.value[}\DecValTok{1}\NormalTok{] }\OtherTok{\textless{}{-}}\NormalTok{ prm\_val.leftmost}
\NormalTok{    result.RMSE[}\DecValTok{1}\NormalTok{] }\OtherTok{\textless{}{-}}\NormalTok{ RMSE.leftmost}
\NormalTok{  \}}
  \ControlFlowTok{if}\NormalTok{ (result.RMSE[n] }\SpecialCharTok{==}\NormalTok{ best\_RMSE) \{}
\NormalTok{    parameter.value[n}\SpecialCharTok{+}\DecValTok{1}\NormalTok{] }\OtherTok{\textless{}{-}}\NormalTok{ prm\_val.rightmost}
\NormalTok{    result.RMSE[n}\SpecialCharTok{+}\DecValTok{1}\NormalTok{] }\OtherTok{\textless{}{-}}\NormalTok{ RMSE.rightmost}
    \CommentTok{\# browser()}
\NormalTok{  \}}

  \FunctionTok{list}\NormalTok{(}\AttributeTok{best\_result =}\NormalTok{ param\_values.best\_result,}
       \AttributeTok{param\_values.endpoints =} \FunctionTok{c}\NormalTok{(prm\_val.leftmost, prm\_val.rightmost, seq\_increment),}
       \AttributeTok{tuned.result =} \FunctionTok{data.frame}\NormalTok{(}\AttributeTok{parameter.value =}\NormalTok{ parameter.value,}
                                 \AttributeTok{RMSE =}\NormalTok{ result.RMSE))}
\NormalTok{\}}
\end{Highlighting}
\end{Shaded}

@@

Sugnature

\hfill\break
- \textbf{fn\_tune.test.param\_value:} A helper function that calculates
the value of the \texttt{RMSE} for a given parameter value.; -
\textbf{break.if\_min = TRUE:} A Boolean parameter that determines
whether the function should terminate after completing the number of
steps specified by the parameter \texttt{steps.beyond\_min}, after the
minimum value of the \texttt{RMSE} has been found; -
\textbf{steps.beyond\_min = 2:} (takes effect only if
\texttt{break.if\_min} parameter is \texttt{TRUE}) Specifies the number
of steps after finding the minimum value of the \texttt{RMSE}, upon
completion of which the function should terminate.

\hfill\break
During execution, the function uses a helper function specified by the
\texttt{fn\_tune.test.param\_value} parameter, which calculates the
\texttt{RMSE} value for the given parameter from the list determined by
the \texttt{param\_values} parameter.

\begin{noteblock}
Note

Source Code

\hfill\break
Below is the most significant part of the code of the \href{}{function}
function:

@@

Sugnature

\hfill\break
- \textbf{fn\_tune.test.param\_value:} A helper function that calculates
the value of the \texttt{RMSE} for a given parameter value.; -
\textbf{break.if\_min = TRUE:} A Boolean parameter that determines
whether the function should terminate after completing the number of
steps specified by the parameter \texttt{steps.beyond\_min}, after the
minimum value of the \texttt{RMSE} has been found; -
\textbf{steps.beyond\_min = 2:} (takes effect only if
\texttt{break.if\_min} parameter is \texttt{TRUE}) Specifies the number
of steps after finding the minimum value of the \texttt{RMSE}, upon
completion of which the function should terminate.

\hfill\break
During execution, the function uses a helper function specified by the
\texttt{fn\_tune.test.param\_value} parameter, which calculates the
\texttt{RMSE} value for the given parameter from the list determined by
the \texttt{param\_values} parameter.

\begin{noteblock}
Note

@@

Source Code

\hfill\break
Below is the most significant part of the code of the \href{}{function}
function:

@@

@@

\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-95-1.pdf}
